---
title: "dendogram-CvsN"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
## Libraries

the libraries that I use

```{r library, include=FALSE}
library(igraph)
library(ggnetwork)
library(tidyr)
library(tibble)
library(gplots)
library(dendextend)
library(tidyverse)
library(RColorBrewer)
```


## My Data

Below you can see the head of my data for a normal sample day. This data has "Date," as you can see, also "Ticker" and "Ticker2" as two-node, and the weight of links is according to the cosine of between these shares.

```{r data, echo=FALSE}

load("/home/bahar/Desktop/project/networkS-P500/data/daily_cosinus_2018.rda")
head(daily_res[1])

```

## Heatmap of normal day

You can see the heatmap of the typical sample day.

```{r heatmap_normal, echo=FALSE}
# heatmap + dendogram for a normal day ------------------------------------
day_network_sample <- daily_res[[1]]
s_day_network_sample <- spread(day_network_sample[,-1], Ticker2, cos_vecs)
s_day_network_sample <- column_to_rownames(s_day_network_sample, var = "Ticker")
s_day_network_sample[is.na(s_day_network_sample)] <- 0
s_day_network_sample <- s_day_network_sample+ t(s_day_network_sample)
s_day_network_sample <- as.matrix(s_day_network_sample)

# custom palette
my_palette <- colorRampPalette(c("red", "purple", "blue"))(n = 299)
# (optional) defines the color breaks manually for a "skewed" color transition
col_breaks = c(seq(-1,-0.3,length=100),  # for red
               seq(-0.3, 0.3,length=100),              # for yellow
               seq(0.3, 1,length=100))              # for green

dist_s_sample <- dist(s_day_network_sample, method="euclidean")
dist_s_sample<- as.matrix(dist_s_sample)
heatmap.2(s_day_network_sample,
          density.info="none",  
          trace="none",         
          margins =c(12,9),    
          col=my_palette,
          dendrogram='both',     
          Rowv=T,
          Colv="Rowv",
          symm= T, revC = identical("Colv", "Rowv")) 


```


## Heatmap of critical day

You can see the heatmap of sample crash day: 

```{r heatmapCrash, echo=FALSE}
# heatmap + dendogram for a crash day -------------------------------------

crash_day <- daily_res[["2018-12-24"]]

crash_day_sample <- spread(crash_day[,-1], Ticker2, cos_vecs)
crash_day_sample <- column_to_rownames(crash_day_sample, var = "Ticker")
crash_day_sample[is.na(crash_day_sample)] <- 0
crash_day_sample <- crash_day_sample + t(crash_day_sample)
crash_day_sample <- as.matrix(crash_day_sample)

# custom palette
my_palette <- colorRampPalette(c("red", "purple", "blue"))(n = 299)
# (optional) defines the color breaks manually for a "skewed" color transition
col_breaks = c(seq(-1,-0.3,length=100),  # for red
               seq(-0.3, 0.3,length=100),              # for yellow
               seq(0.3, 1,length=100))              # for green

dist_crash_day <- dist(crash_day_sample, method="euclidean")
dist_crash_day<- as.matrix(dist_crash_day)
heatmap.2(crash_day_sample,
          density.info="none",  
          trace="none",         
          margins =c(12,9),    
          col=my_palette,
          dendrogram='both',     
          Rowv=T,
          Colv="Rowv",
          symm= T, revC = identical("Colv", "Rowv")) 


```

## clusters

Now we want to count how many clusters we have for a normal sample day.

```{r clusterNormal, echo=FALSE}

  s_day_network_sample <- spread(day_network_sample[,-1], Ticker2, cos_vecs)
  s_day_network_sample <- column_to_rownames(s_day_network_sample, var = "Ticker")
  s_day_network_sample[is.na(s_day_network_sample)] <- 0
  s_day_network_sample <- s_day_network_sample + t(s_day_network_sample)
  
  normal.dist <- as.dist(s_day_network_sample)
  normal.tree <- hclust(normal.dist, method="complete")
  normal.dend <- as.dendrogram(normal.tree) # create dendrogram object
  clusters <- cutree(normal.dend, h=1.5)
  
  table(clusters)

```

plot of this dendogram for normal day is:
```{r dendoN}
plot(color_branches(normal.dend, h=1.5),leaflab="none")
```

Now we want to count how many clusters we have for a sample crash day

```{r clusterCrash, echo=FALSE}
  crash_day <- daily_res[["2018-12-24"]]
  crash_day_sample <- spread(crash_day[,-1], Ticker2, cos_vecs)
  crash_day_sample <- column_to_rownames(crash_day_sample, var = "Ticker")
  crash_day_sample[is.na(crash_day_sample)] <- 0
  crash_day_sample <- crash_day_sample + t(crash_day_sample)
  
  crash.dist <- as.dist(crash_day_sample)
  crash.tree <- hclust(crash.dist, method="complete")
  crash.dend <- as.dendrogram(crash.tree) # create dendrogram object
  clusters <- cutree(crash.dend, h=1.5)
  
  table(clusters)

```

plot of this dendogram for normal day is:
```{r dendoC}
plot(color_branches(crash.dend, h=1.5),leaflab="none")
```
